---
output: github_document
---

# plausibounds

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/plausibounds)](https://CRAN.R-project.org/package=plausibounds)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/plausibounds)](https://r-pkg.org/pkg/plausibounds)
<!-- badges: end -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## Overview

The `plausibounds` package implements methods from [Freyaldenhoven and Hansen (2025)](https://simonfreyaldenhoven.github.io/papers/Plausible_bounds.pdf) to compute restricted bounds for treatment path estimates from event studies and dynamic panel data models. The package provides an alternative solution between pointwise confidence intervals and uniform confidence bands through data-driven surrogate paths that adapt to smoothness and correlation structure.

## Installation

```{r, eval = FALSE}
# Install from CRAN
install.packages("plausibounds")

# Install latest version from GitHub
install.packages("devtools")
devtools::install_github("SimonFreyaldenhoven/plausibounds")
```

## Usage

Find a minimal example below. For more information see the package [documentation](https://cran.r-project.org/package=plausibounds/plausibounds.pdf) and [vignette](https://cran.r-project.org/package=plausibounds/vignettes/documentation.html).

```{r example}
library(plausibounds)
library(ggplot2)

# Load example data
data(estimates_wiggly)
data(var_iid)

# Compute restricted bounds
pb <- plausible_bounds(
  estimates = estimates_wiggly,
  var = var_iid
)

# View results
summary(pb)

# Visualize bounds
create_plot(pb)
```

```{r, eval = FALSE}
# Example with parallel processing
pb_parallel <- plausible_bounds(
  estimates = estimates_wiggly,
  var = var_iid,
  alpha = 0.05,
  parallel = TRUE,
  n_cores = 4
)
```

## Citation

Simon Freyaldenhoven, Christian Hansen. "(Visualizing) Plausible Treatment Effect Paths." Federal Reserve Bank of Philadelphia and University of Chicago, 2025.

Ryan Kobler. "`plausibounds` package." Code and data repository at <https://github.com/SimonFreyaldenhoven/plausibounds>, 2025.
