---
output: github_document
---

# plausibounds

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/plausibounds)](https://CRAN.R-project.org/package=plausibounds)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/plausibounds)](https://r-pkg.org/pkg/plausibounds)
<!-- badges: end -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## Overview

The `plausibounds` package implements the additions to dynamic effect plots suggested in [Freyaldenhoven and Hansen (2026)](https://simonfreyaldenhoven.github.io/papers/Plausible_bounds.pdf). Data-driven smoothing delivers a smooth estimated path with potentially improved point estimation properties and confidence regions covering a surrogate that can be substantially tighter than conventional pointwise or uniform bands.

## Installation

```{r, eval = FALSE}
# Install from CRAN
install.packages("plausibounds")

# Install latest version from GitHub
install.packages("devtools")
devtools::install_github("SimonFreyaldenhoven/plausibounds")
```

## Usage

Find a minimal example below. For more information see the package [documentation](https://cran.r-project.org/package=plausibounds/plausibounds.pdf) and [vignette](https://cran.r-project.org/package=plausibounds/vignettes/documentation.html).

```{r example, results = FALSE, message = FALSE}
library(plausibounds)

# Load example data
data(estimates_bighump)
data(var_bighump)

set.seed(916)

# Compute restricted bounds
pb <- plausible_bounds(
  estimates = estimates_bighump[1:12],
  var = var_bighump[1:12, 1:12]
)
```

```{r view-plot}
# View results
summary(pb)

# Visualize bounds
create_plot(pb)
```

```{r, eval = FALSE}
# Example with parallel processing
pb_parallel <- plausible_bounds(
  estimates = estimates_bighump,
  var = var_bighump,
  alpha = 0.05,
  parallel = TRUE,
  n_cores = 4
)
```

## Citation

Simon Freyaldenhoven, Christian Hansen. "(Visualizing) Plausible Treatment Effect Paths." Federal Reserve Bank of Philadelphia and University of Chicago, 2026.

Simon Freyaldenhoven, Christian Hansen, Ryan Kobler. "`plausibounds` package." Code and data repository at <https://github.com/SimonFreyaldenhoven/plausibounds>, 2026.
